Body size patterns

### 2019-07-12 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
updated plotGams

summary(modBKT)

plot(modBKT, pages = 8, scale = 0)

predGridBKT <- expand.grid(riverFactor = unique(dataIn$riverFactor), 
                        cohortFactor = unique(dataIn$cohort),
                        ydayCumul = seq(250,1000, by = 30),
                        salmon01 = c(0,1),
                        cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

#################################
# Brown trout

modBNT <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) + 
               s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBNT, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledATS, bs = 'cr', k = kIn, by = riverFactor), 
             data = vB %>% filter(cohort %in% 2000:2013, species %in% 'bnt'), method = "REML")

@@

predGridBNT <- expand.grid(riverFactor = unique(dataIn$riverFactor), 
                           cohortFactor = unique(dataIn$cohort),
                           ydayCumul = seq(250,1000, by = 30),
                           salmon01 = c(0,1),
                           cohortStrengthScaledBKT = seq(-2.5,2.5, by = 0.5),
                           cohortStrengthScaledBNT = seq(-2.5,2.5, by = 0.5),
                           cohortStrengthScaledATS = seq(-2.5,2.5, by = 0.5)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

# cohorts by river/species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0
#         (cohortStrengthScaledBKT == 0 & salmon01 == 0) | (cohortStrengthScaledBKT == 0 & cohortStrengthScaledBNT == 0 & cohortStrengthScaledATS == 0 & metaPop01 == 1 & salmon01 ==0)
           ),
#           cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT == 0, cohortStrengthScaledATS == 0, metaPop01 == 1, salmon01 == 0),
       aes(ydayCumul, pred, group = cohort, color = cohort)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
  scale_color_viridis_c(breaks = c(2000,2004,2008,2012), labels = c(2000,2004,2008,2012)) +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  guides(color = guide_colorbar(barheight = 10,
                                barwidth = 1.5,
                                ticks = FALSE,
                                nbin = 100)) +
#  guide_legend(title = 'Cohort') +
  facet_grid(speciesGG ~ riverGG, scales = 'free_y')

>>>>

summary(modBKT)
plot(modBKT, pages = 8, scale = 0)

predGridBKT <- expand.grid(riverFactor = unique(modBKT$model$riverFactor), 
                           cohortFactor = unique(modBKT$model$cohort),
                           ydayCumul = seq(250,1000, by = 30),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

#################################
# Brown trout
# using CSr model becasue delta AIC is not huge btw it and CS3r. Better to have same models for both species
modBNT <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) + 
               s(cohortStrengthScaled, bs = 'cr', k = kIn, by = riverFactor), 
             data = vB %>% filter(cohort %in% 2000:2013, species %in% 'bnt'), method = "REML")

@@

predGridBNT <- expand.grid(riverFactor = unique(modBNT$model$riverFactor), 
                           cohortFactor = unique(modBNT$model$cohort),
                           ydayCumul = seq(250,1000, by = 30),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

# cohorts by river/species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaled == 0
#         (cohortStrengthScaledBKT == 0 & salmon01 == 0) | (cohortStrengthScaledBKT == 0 & cohortStrengthScaledBNT == 0 & cohortStrengthScaledATS == 0 & metaPop01 == 1 & salmon01 ==0)
           ),
#           cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT == 0, cohortStrengthScaledATS == 0, metaPop01 == 1, salmon01 == 0),
       aes(ydayCumul, pred, group = cohort, color = cohort)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
  scale_color_viridis_c(breaks = c(2000,2004,2008,2012), labels = c(2000,2004,2008,2012)) +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  guides(color = guide_colorbar(barheight = 10,
                                barwidth = 1.5,
                                ticks = FALSE,
                                nbin = 100)) +
#  guide_legend(title = 'Cohort') +
  facet_grid(speciesGG ~ riverGG, scales = 'free_y')
